### 2015-10-26 doc/note-to-yaqi/precusor-integration.tex
Fission source term change to precursor-integration note

\be
\frac{C^{n+1}-C^n}{\Delta t}=(1-\theta)\beta(\nu\Sigma_f)^n\varphi^n p^n-(1-\theta)\lambda C^n + \theta\beta(\nu\Sigma_f)^{n+1}\varphi^{n+1}p^{n+1}-\theta\lambda C^{n+1}
\ee

@@

\be
C^{n+1} = \frac{1-(1-\theta)\Delta t\lambda}{1+\theta\Delta t\lambda}C^n + \frac{(1-\theta)\Delta t \beta (\nu\Sigma_f)^n}{1+\theta\Delta t\lambda}\varphi^n p^n +  \frac{(1-\theta)\Delta t \beta (\nu\Sigma_f)^{n+1}}{1+\theta\Delta t\lambda}\varphi^{n+1} p^{n+1}
\ee
Reporting this value of $C^{n+1}$, one can solve for the shape $\varphi^{n+1}$ as a function of $\varphi^n$ and $C^n$
(and $p^n$, $p^{n+1}$, $dp/dt|_n$ and  $dp/dt|_{n+1}$).
Once $\varphi^{n+1}$ has been determined, $C^{n+1}$ is updated. YAK currently implements both implicit and Crank-Nicholson as options for precursor evaluation.

@@

\be
\int_{t_n}^{t_{n+1}} C(t')e^{\lambda t'} dt' = \int_{t_n}^{t_{n+1}} \beta\nu\Sigma_f(t')\varphi(t') p(t')e^{\lambda t'}dt'
\ee

@@

\be
C^{n+1} =  C^n e^{-\lambda (t_{n+1} - t_n) }  + \int_{t_n}^{t_{n+1}} \beta\nu\Sigma_f(t')\varphi(t') p(t')e^{-\lambda (t_{n+1}-t')}dt'
\ee

Because $\beta\nu\Sigma_f$ and $\varphi$ being integrated are not known continuously over the time step, they can be interpolated linearly over the macro step.  Such that:

@@

\be
C^{n+1} = C^n e^{-\lambda \Delta t} 
+ \left(a_3(\beta\nu\Sigma_f)^{n+1}+a_2(\beta\nu\Sigma_f)^n\right)\varphi^{n+1}
+ \left(a_2(\beta\nu\Sigma_f)^{n+1}+a_1(\beta\nu\Sigma_f)^n\right)\varphi^n 
\ee

@@

\underline{``Note-1'':} Applying this procedure to the fission source (assume a linear in time variation for 
$\beta\nu\Sigma_f(t')\varphi(t')$) is simple. We just need to agree what to do with beta.

>>>>

\be
\frac{C^{n+1}-C^n}{\Delta t}=(1-\theta)\beta S_f^np^n-(1-\theta)\lambda C^n + \theta\beta S_f^{n+1}p^{n+1}-\theta\lambda C^{n+1}
\ee

Where $S_f$ is the fission source equivalent for shape:

\be
S_f^n=(\nu\Sigma_f)^n\varphi^n
\ee

@@

\be
C^{n+1} = \frac{1-(1-\theta)\Delta t\lambda}{1+\theta\Delta t\lambda}C^n + \frac{(1-\theta)\Delta t \beta}{1+\theta\Delta t\lambda}S_f^n p^n +  \frac{\theta\Delta t \beta}{1+\theta\Delta t\lambda}S_f^{n+1} p^{n+1}
\ee
Reporting this value of $C^{n+1}$, one can solve for the shape $\varphi^{n+1}$ as a function of $\varphi^n$ and $C^n$
(and $p^n$, $p^{n+1}$, $dp/dt|_n$ and  $dp/dt|_{n+1}$).
Once $\varphi^{n+1}$ has been determined, $C^{n+1}$ is updated. YAK currently implements both implicit and Crank-Nicholson as options for precursor evaluation.

@@

\be
\int_{t_n}^{t_{n+1}} C(t')e^{\lambda t'} dt' = \int_{t_n}^{t_{n+1}} \beta(t') S_f(t') p(t')e^{\lambda t'}dt'
\ee

@@

\be
C^{n+1} =  C^n e^{-\lambda (t_{n+1} - t_n) }  + \int_{t_n}^{t_{n+1}} \beta(t') S_f(t') p(t')e^{-\lambda (t_{n+1}-t')}dt'
\ee

Because $\beta$ and $\nu\Sigma_f\varphi$ being integrated are not known continuously over the time step, they can be interpolated linearly over the macro step.  Such that:

@@

\be
C^{n+1} = C^n e^{-\lambda \Delta t} 
+ \left(a_3\beta^{n+1}+a_2\beta^n\right)S_f^{n+1}
+ \left(a_2\beta^{n+1}+a_1\beta^n\right)S_f^n 
\ee

@@

\underline{``Note-1'':} Applying this procedure to the fission source (assume a linear in time variation for 
$\beta\nu\Sigma_f(t')\varphi(t')$) is simple. We just need to agree what to do with beta. If beta is independent of time, the equation reduces to:

\be
C^{n+1} = C^n e^{-\lambda \Delta t} + \left(\hat{a}_2 S_f^{n+1}+\hat{a}_1 S_f^n\right)\beta
\ee

\begin{align}
&\hat{a}_1= \int_{t_n}^{t_{n+1}}\frac{t_{n+1}-t'}{\Delta t}p(t')e^{-\lambda(t_{n+1}-t')}dt' \\
&\hat{a}_2 = \int_{t_n}^{t_{n+1}}\frac{t'-t_n}{\Delta t}p(t')e^{-\lambda(t_{n+1}-t')}dt'
\end{align}
